Eliminating Systematic Bias in Bright-Siren Multimessenger Observations of Compact Object Mergers from Inclination-Dependent Emission

### 2022-10-06 src/tex/ms.tex
Calculate how much posterior improves when we *know* P_det.

\begin{figure}
    \script{H0-P2.py}
    \includegraphics[width=\columnwidth]{figures/H0-P2.pdf}
    \caption{Posterior on $H_0$ for the mock catalog discussed in \S\,
    \ref{sec:weakly-variable}.  The blue curve is the posterior when fitting
    $P_{\detected,\EM}$ with $N_l = 2$.  The fitted value is $H_0 =
    \variable{output/H0-P2.txt}$ (median and 68\% credible interval).  The
    orange curve is the posterior ignoring inclination-dependent EM selection
    effects, which results in $H_0 = \variable{output/H0-P2-nofit.txt}$, a $\sim
    2\sigma$ bias.  The black vertical line is the true $H_0$ used to generate
    the catalog.}
    \label{fig:H0-P2}
\end{figure}

>>>>

\begin{figure}
    \script{H0-P2.py}
    \includegraphics[width=\columnwidth]{figures/H0-P2.pdf}
    \caption{Posterior on $H_0$ for the mock catalog discussed in \S\,
    \ref{sec:weakly-variable}.  The blue curve is the posterior when fitting
    $P_{\detected,\EM}$ with $N_l = 2$.  We find $H_0 =
    \variable{output/H0-P2.txt}$ (median and 68\% credible interval).  The
    orange curve is the posterior when $P_{\detected,\EM}$ is fixed to its true
    value (i.e.\ we assume we know the EM selection effect perfectly).  We find
    $H_0 = \variable{output/H0-P2-fixed.txt}$, a 5 percent reduction in
    uncertainty.  The green curve is the posterior ignoring
    inclination-dependent EM selection effects, which results in $H_0 =
    \variable{output/H0-P2-nofit.txt}$, a $\sim 2\sigma$ bias.  The black
    vertical line is the true $H_0$ used to generate the catalog.}
    \label{fig:H0-P2}
\end{figure}
